Local PCA results

### 2021-05-20 medicago/summarize_run.Rmd
more stringsAsFactors

# read in mds
mds.coords <- read.csv(mds.file,header=TRUE)
mds.cols <- (1:ncol(mds.coords))[-(1:2)]

# position information
regions <- do.call( rbind, lapply( regions.files, read.csv, header=TRUE ) )
# figure out where to plot things at
chroms <- unique(regions$chrom)
chrom.starts <- tapply( regions$start, regions$chrom, min, na.rm=TRUE )
chrom.ends <- tapply( regions$end, regions$chrom, max, na.rm=TRUE )
chrom.spacing <- floor(.05*mean(chrom.ends))
chrom.offsets <- c(0,cumsum(chrom.spacing+chrom.ends))
names(chrom.offsets) <- c(chroms,"end")
chrom.dividers <- c(0,chrom.offsets[-1])-chrom.spacing/2
chrom.mids <- chrom.dividers[-1] - diff(chrom.dividers)/2

>>>>

# read in mds
mds.coords <- read.csv(mds.file,header=TRUE,stringsAsFactors=TRUE)
mds.cols <- (1:ncol(mds.coords))[-(1:2)]

# position information
regions <- do.call( rbind, lapply( regions.files, read.csv, header=TRUE,stringsAsFactors=TRUE ) )
# figure out where to plot things at
chroms <- unique(regions$chrom)
chrom.starts <- tapply( regions$start, regions$chrom, min, na.rm=TRUE )
chrom.ends <- tapply( regions$end, regions$chrom, max, na.rm=TRUE )
chrom.spacing <- floor(.05*mean(chrom.ends))
chrom.offsets <- c(0,cumsum(chrom.spacing+chrom.ends))
names(chrom.offsets) <- c(chroms,"end")
chrom.dividers <- c(0,chrom.offsets[-1])-chrom.spacing/2
chrom.mids <- chrom.dividers[-1] - diff(chrom.dividers)/2

### 2021-05-20 templated/summarize_run.Rmd
more stringsAsFactors

# read in mds
mds.coords <- read.csv(mds.file,header=TRUE)
mds.cols <- (1:ncol(mds.coords))[-(1:2)]

# position information
regions <- do.call( rbind, lapply( regions.files, read.csv, header=TRUE ) )
# figure out where to plot things at
chroms <- unique(regions$chrom)
chrom.starts <- tapply( regions$start, regions$chrom, min, na.rm=TRUE )
chrom.ends <- tapply( regions$end, regions$chrom, max, na.rm=TRUE )
chrom.spacing <- floor(.05*mean(chrom.ends))
chrom.offsets <- c(0,cumsum(chrom.spacing+chrom.ends))
names(chrom.offsets) <- c(chroms,"end")
chrom.dividers <- c(0,chrom.offsets[-1])-chrom.spacing/2
chrom.mids <- chrom.dividers[-1] - diff(chrom.dividers)/2

>>>>

# read in mds
mds.coords <- read.csv(mds.file,header=TRUE, stringsAsFactors=TRUE)
mds.cols <- (1:ncol(mds.coords))[-(1:2)]

# position information
regions <- do.call( rbind, lapply( regions.files, read.csv, header=TRUE, stringsAsFactors=TRUE ) )
# figure out where to plot things at
chroms <- unique(regions$chrom)
chrom.starts <- tapply( regions$start, regions$chrom, min, na.rm=TRUE )
chrom.ends <- tapply( regions$end, regions$chrom, max, na.rm=TRUE )
chrom.spacing <- floor(.05*mean(chrom.ends))
chrom.offsets <- c(0,cumsum(chrom.spacing+chrom.ends))
names(chrom.offsets) <- c(chroms,"end")
chrom.dividers <- c(0,chrom.offsets[-1])-chrom.spacing/2
chrom.mids <- chrom.dividers[-1] - diff(chrom.dividers)/2
